The K2 Bright Star Survey

### 2019-05-31 paper/ms.tex
greklek-mckeon on paper
36 oph is active

@@

In order to choose the values for $k$ and $\delta$ in our objective function, we used the quiet system 36~Ophiuchi (Guniibuu, $V= 5.08$), a K1/K2/K5 main sequence triple system consisting of the lowest-mass main sequence stars in the sample of stars with halo apertures. Very little high frequency variability is detected or predicted. It was also observed at short cadence. We chose the 6.5~hour Combined Differential Photometric Precision \citep[CDPP,][]{cdpp} as implemented in \texttt{lightkurve} \citep{lightkurve} as a proxy for the `noise' in a light curve, with lower being better.

>>>>

\author[0000-0002-0371-1647]{Michael Greklek-McKeon}
\affiliation{Institute for Astronomy, University of Hawai\okina i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA}

@@

In order to choose the values for $k$ and $\delta$ in our objective function, we used the system 36~Ophiuchi (Guniibuu, $V= 5.08$), a K1/K2/K5 active main sequence triple system consisting of the lowest-mass main sequence stars in the sample of stars with halo apertures. Very little high frequency variability is detected or predicted. It was also observed at short cadence. We chose the 6.5~hour Combined Differential Photometric Precision \citep[CDPP,][]{cdpp} as implemented in \texttt{lightkurve} \citep{lightkurve} as a proxy for the `noise' in a light curve, with lower being better.
